### 2014-07-15 Paper.tex
Added Section 4

\begin{defn}
For $\Gamma$ a diagram of finite type, we define the associated Artin Group as follows. The associated artin group $W_\Gamma$ is generated by $s_i,$ where there is one $s_i$ for each vertex $i$ in $\Gamma.$ These generators are subject to the relations
\begin{itemize}
	\item[(R2')] For all $i \neq j,$ we add the relations
	\\
$	\begin{cases}
	s_is_j=s_js_i, &\text{ if there is no edge between $i$ and $j$}\\
	s_is_js_i = s_js_is_j &\text{ if there is an edge of weight 1 between $i$ and $j.$}\\
	s_is_js_is_j = s_js_is_js_i &\text{ if there is an edge of weight 2 between $i$ and $j$.}\\
	s_is_js_is_js_is_j = s_js_is_js_is_js_i &\text{ if there is an edge of weight 3 between $i$ and $j$.}
\end{cases}$
\item[(R3')(a)] For every chordless cycle of the form

@@

>>>>

\begin{defn} \label{grp def}
For $\Gamma$ a diagram of finite type, we define the associated Artin Group as follows. The associated artin group $W_\Gamma$ is generated by $s_i,$ where there is one $s_i$ for each vertex $i$ in $\Gamma.$ These generators are subject to the relations
\begin{itemize}
	\item[(R2')] For all $i \neq j,$ we add the relations
	\\
$	\begin{cases}
	s_is_j=s_js_i, &\text{ if there is no edge between $i$ and $j$}\\
	s_is_js_i = s_js_is_j &\text{ if there is an edge of weight 1 between $i$ and $j.$}\\
	s_is_js_is_j = s_js_is_js_i &\text{ if there is an edge of weight 2 between $i$ and $j$.}\\
	s_is_js_is_js_is_j = s_js_is_js_is_js_i &\text{ if there is an edge of weight 3 between $i$ and $j$.}
\end{cases}$
\item[(R3')(a)] For every chordless cycle of the form

@@

\section{Symmetry among (R3') Relations}

As in \cite{Barot}, given the relations (R2'), many of the relations in (R3')(a) and (b) become redundant. For example,

\begin{lem}
Let $\Gamma$ be a diagram of finite type which contains a chordless cycle C:
\begin{tikzcd}
i_0 \arrow{r} & i_1 \arrow{r} & \cdots \arrow{r} & i_{d-1} \arrow{r} & i_0
\end{tikzcd}
so that all edges have weight 1. Then if W is a group generated by $s_{1}, \dots, s_{n}$ satifying the relations (R2') and r(i_{a}, i_{a+1}) for some a $\in \{1, \dots, d\}$, all of the relations in (R3)(a) hold for C.
\end{lem}

\begin{proof}
As in Barot-Marsh, it suffices to prove that the relation r(0, 1) implies the relation r(d-1, 0). So suppose $W_{\gamma}$ satisfies the relation r(0, 1). Then we have 
\begin{align*}
& s_{d-1}s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_1s_0 \\
&= s_{0}^{-1}s_{0}s_{d-1}s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{d-1}^{-1}s_{0}s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{d-1}^{-1}s_{0}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-1}s_{d-2}s_{d-1}^{-1}s_{d-3}\dots s_{1}s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{d-1}^{-1}(s_{0}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}^{-1}s_{d-1}s_{d-2}s_{d-3}\dots s_{1})s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{d-1}^{-1}(s_{1}^{-1} \dots s_{d-2}^{-1}s_{d-1}s_{d-2}s_{d-3}\dots s_{0})s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{d-1}^{-1}(s_{1}^{-1} \dots s_{d-3}^{-1}s_{d-1}s_{d-2}s_{d-1}^{-1}s_{d-3}\dots s_{0})s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{0}s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{0}s_{d-1}s_{0}^{-1}s_{0} \\
&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{0}s_{d-1} 
\end{align*}
as required. Note that line 3 is equal to 4 and line 7 is equal to line 8 since the cycle is chordless, meaning that $s_{d-1}$ commutes with every element except $s_{0}$ and $s_{d-2}$.
\end{proof}

Furthermore, we obtain similar results for cycles containing edges of weight 2.

\begin{lem} 
Let $\Gamma$ be a diagram of finite type containing a 3-cycle as in (R3')(b) of ~\ref{grp def}. Let W be the group with generators $s_{1}, \dots, s_{n}$ defined by $\Gamma$. Then the relations (1) and (2) of (R3')(b) are equivalent, and they together imply the relation (3).
\end{lem}

\begin{proof}
The equivalence of (1) and (2) follows from the fact that
\begin{align*}
& s_{1}^{-1}s_{3}s_{2}s_{3}^{-1}s_{1}s_{3}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1}s_{3}s_{3}^{-1}s_{1} \\
&= s_{1}^{-1}s_{3}s_{2}s_{3}^{-1}s_{1}s_{3}s_{2}^{-1}s_{3}^{-1} \\
&= s_{1}^{-1}s_{2}^{-1}s_{3}s_{2}s_{1}s_{2}^{-1}s_{3}^{-1}s_{2}
\end{align*}

In showing that (1) and (2) imply (3), we will underline the terms being manipulated in each line for emphasis.
\begin{align*}
& s_{1}s_{3}s_{1}(s_{3}^{-1}s_{1}^{-1}s_{2}s_{1}s_{3}s_{1}^{-1}s_{2}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{1})s_{1}^{-1}s_{3}^{-1}s_{1}^{-1} \\
&= s_{1}\underline{s_{3}s_{1}s_{3}^{-1}s_{1}^{-1}}s_{2}s_{1}s_{3}s_{1}^{-1}s_{2}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}\underline{s_{1}s_{1}^{-1}}s_{3}^{-1}s_{1}^{-1} \\
&= \underline{s_{1}s_{1}^{-1}}\underline{s_{3}^{-1}s_{1}s_{3}s_{2}}s_{1}s_{3}s_{1}^{-1}s_{2}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
&= s_{2}\underline{s_{3}^{-1}s_{1}s_{3}s_{1}}s_{3}s_{1}^{-1}s_{2}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
&= s_{2}s_{1}s_{3}\underline{s_{1}s_{3}^{-1}s_{3}s_{1}^{-1}}s_{2}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
&= s_{2}\underline{e}s_{1}s_{3}s_{2}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
&= s_{2}s_{3}\underline{s_{3}^{-1}s_{1}s_{3}s_{2}}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
&= \underline{s_{2}s_{3}s_{2}}s_{3}^{-1}s_{1}s_{3}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
&= s_{3}s_{2}\underline{s_{3}s_{3}^{-1}}s_{1}\underline{s_{3}s_{1}s_{3}^{-1}s_{1}^{-1}}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
&= s_{3}s_{2}\underline{s_{1}s_{1}^{-1}}\underline{s_{3}^{-1}s_{1}s_{3}s_{2}^{-1}}s_{3}^{-1}s_{1}^{-1} \\
&= s_{3}\underline{s_{2}s_{2}^{-1}}s_{3}^{-1}s_{1}\underline{s_{3}s_{3}^{-1}}s_{1}^{-1} \\
&= \underline{s_{3}s_{3}^{-1}}\underline{s_{1}s_{1}^{-1}} \\
&= e
\end{align*}
\end{proof}

\begin{lem} 
Let $\Gamma$ be a diagram of finite type containing a 4-cycle as in (R3')(c) of ~\ref{grp def}. Let W be the group with generators $s_{1}, \dots, s_{n}$ defined by $\Gamma$. Then the relations (1) and (2) of (R3')(c) are equivalent.
\end{lem}

\begin{proof}
We have that
\begin{align*}
& s_{3}^{-1}s_{4}^{-1}s_{2}(s_{1}s_{2}^{-1}s_{3}^{-1}s_{4}s_{3}s_{2}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{4}^{-1}s_{3}s_{2})s_{2}^{-1}s_{4}s_{3} \\
&= s_{3}^{-1}s_{4}^{-1}(s_{2}s_{1}s_{2}^{-1})(s_{3}^{-1}s_{4}s_{3})(s_{2}s_{1}^{-1}s_{2}^{-1})s_{3}^{-1}s_{4}^{-1}s_{3}s_{4}s_{3} \\
&= s_{3}^{-1}s_{4}^{-1}s_{1}^{-1}s_{2}s_{1}s_{4}s_{3}s_{4}^{-1}s_{1}^{-1}s_{2}^{-1}s_{1}s_{3}^{-1}(s_{4}^{-1}s_{3}s_{4})s_{3} \\
&= s_{3}^{-1}s_{4}^{-1}s_{1}^{-1}s_{2}s_{1}s_{4}s_{3}s_{4}^{-1}s_{1}^{-1}s_{2}^{-1}s_{1}s_{4}
\end{align*}
\end{proof}

Finally, we conclude the section by establishing a relationship between the groups defined by $\Gamma$ and $\Gamma^{op}$.

\begin{lem} (Analogue of 4.6) 
Let W$_{\Gamma}$ be generated by $s_{1}, \dots, s_{n}$. Then $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfy the relations (R2') and (R3') in W$_{\Gamma^{op}}$.
\end{lem}
\begin{proof}
One can see that the elements satisfy (R2') in W$_{\Gamma^{op}}$ by taking the inverse of both sides of the relation in W$_{\Gamma}$. To see that the elements satisfy (R3') in W$_{\Gamma^{op}}$, note that for a chordless cycle in $\Gamma$ with all weights equal to one, we have $$s_{0}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{0} = s_{1}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{1}$$ by the relation r(0,1) in (R3') in W$_{\Gamma}$. But then applying relations from (R2'), we have that $$s_{0}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{0} = s_{1}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{1},$$ and since the cycle in chordless, we then have $$s_{0}^{-1}s_{d-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{d-1}^{-1}s_{0} = s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}.$$ Repeating this process, we find that $$s_{0}^{-1}s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}s_{0} = s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}.$$ But this can only occur if $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfies the relation r'(0, d-1) in W$_{\Gamma^{op}}.$

For a triangle as in (R3')(b) of ~\ref{grp def}, by the relation r'(1, 2) we have $$s_{1}s_{2}^{-1}s_{3}s_{2}s_{1}^{-1} = s_{2}^{-1}s_{3}s_{2}.$$ Hence $$s_{1}s_{3}s_{2}s_{3}^{-1}s_{1}^{-1} = s_{3}s_{2}s_{3}^{-1}.$$ But as before, this can occur if and only if $s_{1}^{-1}, s_{2}^{-1}, s_{3}^{-1}$ satisfy the relation r'(1, 3) in W$_{\Gamma^{op}}$.

Finally, given a square labeled as in (R3')(c) and the relations r'(1, 2) and r'(3, 4), we have 
\begin{align*}
& s_{2}s_{1}s_{4}s_{3}s_{4}^{-1}s_{1}^{-1} \\
&= s_{1}s_{1}^{-1}s_{2}s_{1}s_{4}s_{3}s_{4}^{-1}s_{1}^{-1} \\
&= s_{1}s_{2}s_{1}s_{2}^{-1}s_{3}^{-1}s_{4}s_{3}s_{1}^{-1} \\
&= s_{1}s_{2}(s_{1}s_{2}^{-1}s_{3}^{-1}s_{4}s_{3}s_{2})s_{2}^{-1}s_{1}^{-1} \\
&= s_{1}s_{2}(s_{2}^{-1}s_{3}^{-1}s_{4}s_{3}s_{2}s_{1})s_{2}^{-1}s_{1}^{-1} \\
&= s_{1}s_{4}s_{3}s_{4}^{-1}s_{2}s_{2}^{-1}s_{1}^{-1}s_{2} \\
&= s_{1}s_{4}s_{3}s_{4}^{-1}s_{1}^{-1}s_{2}
\end{align*}
But this relation holds if and only if $s_{1}^{-1}, \dots, s_{4}^{-1}$ satisfy r'(2, 1) in W$_{\Gamma^{Op}}$. Therefore, we are done.
\end{proof}

\section{Main Results}
